### 2014-01-21 inst/doc/README.Rmd
update installation of suggested packages notes

While the dependencies for basic functionality are kept to a minimum, to access all the functions and tests implemented in `EML` you'll need several additional packages.

```r
install.packages(c("yaml", "knitr", "rfigshare", "testthat", "RCurl"))
```

@@

```r
install.packages("uuid")
install_github("RHTMLForms", "omegahat")
install_github("XMLSchema", "omegahat")
```

>>>>

While the dependencies for basic functionality are kept to a minimum, to access all the functions and tests implemented in `EML` you'll need several additional packages from CRAN.

```r
install.packages(c("knitr", "rfigshare", "testthat", "RCurl", "dataone"))
```

@@

```r
install_github("RHTMLForms", "omegahat")
install_github("XMLSchema", "omegahat")
```
